\documentclass{article}

\begin{document}

\subsection{Email}

\textbf{Please do not email the TAs for help.} I have assigned them enough duties. I only provide their email addresses above in case you have trouble figuring out the Zoom office hours and might need to email the TAs for help on that.

\textbf{You can email me for help at either \textbf{apksingh@ucdavis.edu} or \textbf{aarons.7007@gmail.com}}. I usually end up responding with \textbf{aarons.7007@gmail.com}. I try to check my email at least once a day. \textbf{Please prefer email over Canvas messages}; Canvas messages are less convenient on my end, so I sometimes check them less often. If I do not respond after a certain period of time (perhaps a day or so), feel free to resend the email. \textbf{\textit{Don't be afraid of asking too many questions over email, either.}} If you email me for help and then find that you no longer need help, please respond to the email you sent to me and tell me that you no longer need help, so that I don't waste time responding to an email that you no longer need a response to. Please include the course (ECS 34 or ECS 50) at the start of the subject line, since I am teaching two courses this quarter.

Assisting a student over email is obviously more difficult than it is during office hours, so if you ever find yourself considering skipping office hours since you can ``email me later anyways,'' I would recommend against that.

\textbf{Please heed the following when emailing me:}

\begin{itemize}[itemsep=0mm,parsep=0pt]
\item Use your UC Davis email address, so that I know it is you.
\item If you need to send me code, please do so in one of the below ways. Do not send me an image, because if I wish to try your code, I would have to retype it, which I won't do.
    \begin{itemize}[itemsep=0mm, parsep=0pt]
    \item You can tell me that your most recent code is in your last Gradescope submission. (If you are doing more submissions after emailing me, then it would probably help if you told me a submission number, timestamp, and/or URL.) I can then view your code on Gradescope.
    \item You can send the code file(s). 
    \item You can copy/paste the file into your email. (I wouldn't do this if there are multiple files.)
    \end{itemize}
\item Give me some idea of what issues you are experiencing (e.g. error messages) and (if applicable) what you have tried. The goal is to help me help you. Don't just say that the code doesn't work; I may ignore emails that do this.
\item Be patient if I respond back with questions or with not much to say. Sometimes, some email chains end up having to be back-and-forths (because I don't simply give away answers; I guide you to them). Other times, one response from me is sufficient. That said, email has limitations, and this is why we have office hours.
\end{itemize}

And don't forget: you can email me conceptual questions as well (not just homework help) or for general advice on computer science or college. I care about your success not just in this class but outside of it as well.

\end{document}
