\documentclass{article}

\begin{document}

\subsubsection{OH Layout (Zoom)}

\textbf{Office hours will be held over Zoom; see the Zoom tab in the navigation panel of the Canvas.} When you access an OH meeting over Zoom, it should give you the option of either using the Zoom desktop application or using Zoom in the browser; pick whichever you prefer. While we will not require that you have your webcam on during office hours, we do require that you have your microphone on, because if we have to communicate with you over chat, then you might as well email for help at that point.

The structure of the office hours will be controlled by the host(s), whether me or one of the TAs. There are two feasible configurations permitted by Zoom, as explained below. These options should not significantly affect the office hours experience but just provide some organizational flexibility. Depending on the number of students in the OH, the nature of the questions being asked, and other factors, one OH format may be more convenient than the other, but again, this is all up to the OH host.

\begin{itemize}[itemsep=0mm, parsep=0pt]
\item \textbf{Breakout rooms}: With the breakout rooms setting, all students can log into the Zoom session, and the host can answer questions and talk to all of the attendants simultaneously. In situations in which it is preferable for the host and a student to speak in private (e.g. so that the student can show their code), then the host and the student will go into what Zoom calls a ``breakout room'', in which the host and the student can converse and share screens without the other students in the meeting seeing this.
\item \textbf{Waiting room}: With this Zoom setting, the host manually lets the next student into the Zoom meeting. Until you are let in, you will simply see a screen informing you that the host is currently with another student. Once the host is ready, they will let you into the meeting and assist you. If you are in the waiting room, you should wait instead of leaving the meeting and checking back in every now and then; the problem with doing the latter is that you will lose your spot in line. Unfortunately, Zoom does not permit us to make the waiting room's members visible to the students, but I do periodically try to post the line in the waiting room chat so that students get some idea of how long they may have to wait.
\end{itemize}

My OH will be recorded, but this recording will only be accessible by me. This is for my own protection, for the same reason that an instructor never closes the door while talking to a student in their office. I have told my TA(s) that they can do the same, if they wish.

\end{document}
